---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# searchbuilder

<!-- badges: start -->
<!-- badges: end -->

The goal of searchbuilder is to identify overrepresented terms in a set of relevant references for a systematic review or evidence synthesis in general, which can then be applied in a boolean search in a bibliograpic database (e.g. PubMed).

## Installation
You can install searchbuilder from GitHub. The package is currently not released on CRAN, but will be in the future.
```{r installation}
library(remotes)
remotes::install_github("https://github.com/IQWiG/searchbuilder")

```

## Example

This is a basic example which shows you how to solve a common problem, the package was designed for:

```{r example}
library(searchbuilder)
path <- system.file("extdata", "example_ris.txt", package= "searchbuilder", mustWork = T)
data <- z_scores(path)
head(print_z_scores(data, terms = "freetext") )
head(print_z_scores(data, terms = "MeSH"))
```
