---
title: "z_scores"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{z_scores}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(searchbuildR)
```
This package provides an easy-to use wrapper for a textual analysis of potential search terms for scientific publications including an analysis of MeSH-Terms following the methodolgy of Hausner, et al. (2011)

Import a set of references, that serve as a testset of potentially relevant studies of the review as a risfile. The argument `"dev_set"` let's you control, whether your testset should be split up in a 2:1 ratio into a development set (used for calculating the z-scores) and a validation set.

```{r create testset, include = TRUE, eval = FALSE}
testsetPubMed <- create_testset("inst/extdata/testset_pubmed.txt")
```

You can either use the default population set integrated in searchbuildR: 
```{r import references, include = TRUE}

testset <- z_scores(references = testsetPubMed)
```

Or you can create your own population set based on a RIS or PubMed format file:
```{r create custom population set, inlcude = TRUE, eval = FALSE}
popset2022 <- create_popset("path/to/populationSet.txt")
```

And calculate the z-scores based on your custom population set:
```{r calculate custom zscores, include = TRUE}

custom_z_scores <- z_scores(references = testsetPubMed, custom_popset = popset2022)

```


```{r show tables, include=TRUE,}

head(testset$freetext)
head(testset$MeSH)
head(testset$qualifier)
```

